---
title: "API_test"
author: "JialongLi"
date: "2022-11-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# API and Data Cleanning


```{r imports, include=FALSE}
# run this chunk_1
library(httr)
library(jsonlite)
library(rvest)
# I didn't use data.table for this time, cuz I only get 1,000 rows of data.
# Maybe we should use it later because it's much faster that tidyverse
# Reference: https://jtr13.github.io/cc21fall2/comparison-among-base-r-tidyverse-and-datatable.html
library(tidyverse)
library(stringi)

GETfunc = function(URL) {
  GET(
    url = URL,
    config = add_headers(
      "Host" = "data.usajobs.gov",
      "User-Agent" = "jialong7@illinois.edu",
      "Authorization-Key" = "Cuht8z1/tYxh7Lr6pfdk24oXpYddEeKjD0kUkBHFfgE="
    )
  )
}

Search_query = function(Key_word, location, URL) {
  # remove block, keep only alphatic (sometimes input is "New York")
  Key_word = stri_replace_all_fixed(Key_word, " ", "")
  location = stri_replace_all_fixed(location, " ", "")
  query = paste0(URL,"?Keyword=",Key_word,"&LocationName=",location,"&ResultsPerPage=1000")
  query
}

# key_word = "data", location = "champagin", URL is fixed, "https://data.usajobs.gov/api/search".
test_query_1 = Search_query("data", "NYC","https://data.usajobs.gov/api/search")
read = GETfunc(test_query_1)
data = fromJSON(rawToChar(read$content))
# data

# an example, to run our code
# test_query_2 = Search_query("data", "New York", "https://data.usajobs.gov/api/search")
# read = GETfunc(test_query_2)
# data = fromJSON(rawToChar(read$content))
# data

GetDataFrame = function(query) {
  # read data
  read = GETfunc(query)
  data = fromJSON(rawToChar(read$content))
  Research_result = data$SearchResult$SearchResultItems$MatchedObjectDescriptor
  selected_df = Research_result |>
    select(PositionTitle, PositionLocationDisplay, OrganizationName, DepartmentName)
  
  # columns in first layer
  result_df = selected_df |>
    select(PositionTitle, PositionLocationDisplay, PositionLocationDisplay, OrganizationName, DepartmentName)
  
    for (i in 1:nrow(result_df)) {
    salary_range = unlist(data$SearchResult$SearchResultItems$MatchedObjectDescriptor$PositionRemuneration[i])
    result_df$MinimumRange[i] = salary_range[[1]]
    result_df$MaximumRange[i] = salary_range[[2]]
    }
  
  # add columns from deeper layer. 
  text = rep(0,nrow(Research_result))
  x = rep(0,nrow(Research_result))
  y = rep(0,nrow(Research_result))
  Education_degree = rep(0,nrow(Research_result))
  for(i in 1:nrow(Research_result)) {
    # gpa requirement
    text[i] = Research_result$QualificationSummary[[i]]
    x[i] = unlist(str_extract_all(text[i], "[\\d]+[\\.]+[\\d]+[\\/]+[\\d]+[\\.]+[\\d]"))[1]
    y[i] = as.numeric(str_split(x[i], pattern = "/")[[1]])[1]
    
    # education degree
    Education_degree[i] = str_extract(text[i],"([B|b]+[a]+[c]+[h]+[e]+[l]+[o]+[r])|([M|m]+[a]+[s]+[t]+[e]+[r])|([B|b]+[a]+[c]+[c]+[a]+[l]+[a]+[u]+[r]+[e]+[a]+[t]+[e])|([G|g]+[r]+[a]+[d]+[u]+[a]+[t]+[e])+([D|d]+[o]+[c]+[t]+[o]+[r])|([P|p]+[H|h]+[\\.]+[D|d])|([D|d]+[o]+[c]+[t]+[o]+[r]+[a]+[l])")
  }
  
  # need 3.0 instead of 3
  GPA_requirement = ifelse(is.na(y),"GPA not required",sprintf("%.1f",y))
  result_df = cbind(result_df,GPA_requirement)
  
  # standardized terms we use
  Education_degree = ifelse(is.na(Education_degree),"not required",Education_degree)
  Education_degree = ifelse(toupper(Education_degree) == "BACCALAUREATE", "bachelor", Education_degree)
  Education_degree = ifelse(toupper(Education_degree) == "PH.D", "doctoral", Education_degree)
  Education_degree = str_to_lower(Education_degree)
  result_df = cbind(result_df,Education_degree)
  
  result_df
}

# The DF
selected_df = GetDataFrame(test_query_1)
```



```{r}
selected_df |>
  select(Education_degree) |>
  group_by(Education_degree) |>
  summarise(n = n())
```


```{r}
visualization = function(selected_df, by) {
  # Location
  if (by == "PositionLocationDisplay") {
    plot = selected_df |>
      group_by(PositionLocationDisplay) |>
      summarise("Job Location" = n()) |>
      ggplot(aes(x=`PositionLocationDisplay`, y=`Job Location`, fill=`PositionLocationDisplay`)) +
      geom_bar(stat = "identity") +
      labs(x = "Jobs locations", y="Counts") +
      theme_bw() +
      theme(panel.grid = element_blank()) +
      theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7)) +
      scale_y_continuous(breaks=seq(0, 300, 50)) +
      guides(fill=guide_legend(title="Job locations"))
    return(plot)
  }
  
  # Department Name
  if (by == "Department Name") {
    plot = selected_df |>
      group_by(DepartmentName) |>
      summarise("y" = n()) |>
      ggplot(aes(x = `DepartmentName`, y =`y`, fill = `DepartmentName`)) +
      geom_bar(stat = "identity") +
      labs(x="Department Name", y="Counts") +
      theme_bw() +
      theme(panel.grid = element_blank()) +
      theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7)) +
      scale_y_continuous(breaks = seq(0, 300, 50)) +
      guides(fill=guide_legend(title = "Department Name"))   
    return(plot)
  }
  
  # Educational Degree
  if (by == "Education degree") {
    plot = selected_df |>
      group_by(Education_degree) |>
      summarise(y = n()) |>
      ggplot(aes(x=`Education_degree`, y=`y`, fill=`Education_degree`)) +
      geom_bar(stat = "identity") +
      labs(x="Education degree", y= "Counts") +
      theme_bw() +
      theme(panel.grid = element_blank()) +
      theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7)) +
      scale_y_continuous(breaks=seq(0, 300, 50)) +
      guides(fill=guide_legend(title="Educational reuirements"))   
    return(plot)
  }
  print("bug")
}
visualization(selected_df,"PositionLocationDisplay")
visualization(selected_df,"Department Name")
visualization(selected_df,"Education degree")
```


functionality: App title should indicate that the data is for data-oriented jobs, not all USA jobs. 
| beauty: Data viz text is too small to read. Consider increasing font size of text in data viz. Colors in data viz are distracting and vertical bars are harder to visually distinguish than horizontal bars. Consider a single color for all bars and orienting the bars horizontally. Also consider adding text to show the counts among the bars, e.g., at the top of the bars.	

```{r}
# Job Locations
cutted = selected_df %>%
  select(PositionLocationDisplay) %>%
  arrange()

for (i in 1:length(cutted$PositionLocationDisplay)) {
  string = cutted$PositionLocationDisplay[i]
  shorted = str_remove_all(string, ", United States")
  shorted1 = str_remove_all(shorted, "May be filled in ")
  shorted2 = str_remove_all(shorted1, "(remote job)")
  shorted3 = str_remove_all(shorted2, "[()]")
  shorted4 = str_remove_all(shorted3, " Upon Request")
  shorted5 = str_remove_all(shorted4, " After Selection")
  cutted$PositionLocationDisplay[i] = shorted5
}

cutted %>%
  group_by(PositionLocationDisplay) %>%
  summarise("y" = n()) %>%
  arrange(desc(y)) |>
  slice_head(n = 7) |>
  ggplot(aes(x=reorder(`PositionLocationDisplay`,+`y`), y=`y`)) +
  coord_flip() + 
  geom_bar(stat = "identity") +
  geom_text(aes(label= y), hjust = -0.3, size = 3.5) +
  labs(x="Jobs Location", y="Jobs offered") +
  theme_light() +
  theme(panel.grid = element_blank(), text = element_text(size = 20)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 13)) +
  scale_y_continuous(breaks=seq(0, 300, 50)) +
  guides(fill=guide_legend(title="Job locations"))
```

```{r}
# keep only 8 biggest.
cutted = selected_df %>%
  group_by(DepartmentName) %>%
  summarise("y" = n()) %>%
  arrange(desc(y)) %>%
  slice_head(n=7)
# 
for (i in 1:length(cutted$DepartmentName)) {
  string = cutted$DepartmentName[i]
  shorted = str_remove_all(string, "Department of ")
  if (shorted == "Other Agencies and Independent Organizations") shorted = "Other Agencies"
  if (shorted == "Health And Human Services") shorted = "Health & Human Services"
  cutted$DepartmentName[i] = shorted
}
  cutted |>
  ggplot(aes(x=reorder(`DepartmentName`,+`y`), y=`y`)) +
  coord_flip() + 
  geom_bar(stat = "identity") +
  geom_text(aes(label= y), hjust = -0.3, size = 3.5) +
  labs(x="Department Name", y="Jobs offered") +
  theme_light() +
  theme(panel.grid = element_blank(), text = element_text(size = 20)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks=seq(0, 275, 50)) +
  guides(fill=guide_legend(title="Department Name"))
```


```{r}
selected_df %>%
  group_by(Education_degree) %>%
  summarise("y" = n()) %>%
  arrange(desc(y)) %>%
  slice_head(n = 8) %>%
  ggplot(aes(x=reorder(`Education_degree`,+`y`), y=`y`)) +
  coord_flip() + 
  geom_bar(stat = "identity") +
  geom_text(aes(label= y), hjust = -0.3, size = 4) +
  labs(x="Minimum educational degree", y="Jobs offered") +
  theme_light() +
  theme(panel.grid = element_blank(), text = element_text(size = 20)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks=seq(0, 470, 50)) +
  guides(fill=guide_legend(title="Education degree"))
```


